
---
title: "Idiosyncratic Risk-Adjusted Sales Growth Forecast: A Copula-Based Approach"

abstract: "Abstract"
author: "Ekaterina Smirnova"

output: 
  word_document:
    pandoc_args: ["--lua-filter=multiple-bibliographies.lua","-Fpandoc-crossref"]
    reference_docx: template.docx
csl: 'style.csl'
bibliography: ["packages.bib","literature.bib"]
---

```{r setup, include=FALSE, eval=T}

rm(list=ls())
setwd("D:/...")
Sys.setenv(LANGUAGE='en')

Packages <- c("knitr",
              "dplyr",
              "flextable",
              "officer",
              "readr",
              "ggplot2",
              "captioner",
              'tibble',
              "tidyverse",
              "factoextra",
              'RColorBrewer',
              "VineCopula",
              "officedown",
              "data.table",
              "fuzzyjoin",
              "igraph",
              "caret",
              "VGAM",
              "scales",
              "shiny", 
              "rvinecopulib",
              "hablar",
              "tmvnsim",
              "CDVine",
              "paleotree",
              "sjmisc",
              "janitor",
              "knitcitations", 
              "pastecs",
              "zoo",
              "ggpubr",
              "ggplotify",
              "reticulate",
              "fitdistrplus",
              "ggrepel",
              "tidyr")
invisible(lapply(Packages,library,character.only=TRUE))


cleanbib()
options("citation_format" = "pandoc")

```

```{r echo=FALSE, include=FALSE, results="hide"}
## Dummy block to stop R check failing when it tries to tangle and source the vignette
citep(citation("knitr"))
citet("10.1098/rspb.2013.1372")
```

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```


```{r message=FALSE, warning=FALSE, include=FALSE, eval=T}

figure_nums <- captioner(prefix = "Picture", suffix=". ")

figure_nums(name = "positions", caption = "Caption")

figure_nums(name ="markets", caption="Markets")

```


```{r message=FALSE, warning=FALSE, include=FALSE, eval=T}

table_nums <- captioner(prefix = "Table",suffix=". ")

table_nums(name="challenges", caption="Caption 1")

table_nums(name="variables", caption="Caption 2")

```

\newpage

# [Introduction]

`r tufte::quote_footer('citation')`

<br/><br/>

R packages and sources citations *R* [@R-base]: *knitr* `r citep(citation("knitr"))`, *dplyr* `r citep(citation("dplyr"))`, *flextable* `r citep(citation("flextable"))`, *officer* `r citep(citation("officer"))`, *readr* `r citep(citation("readr"))`, *ggplot2* `r citep(citation("ggplot2"))`, *captioner* `r citep(citation("captioner"))`, *tibble* [@R-tibble], *tidyverse* `r citep(citation("tidyverse"))`, *factoextra* `r citep(citation("factoextra"))`, *RColorBrewer* `r citep(citation("RColorBrewer"))`, *VineCopula* `r citep(citation("VineCopula"))`, *officedown* `r citep(citation("officedown"))`, *data.table* `r citep(citation("data.table"))`, *fuzzyjoin* `r citep(citation("fuzzyjoin"))`, *igraph* `r citep(citation("igraph"))`, *tidyr* `r citep(citation("tidyr"))`, *caret* `r citep(citation("caret"))`, *VGAM* `r citep(citation("VGAM"))`, *scales* `r citep(citation("scales"))`, *shiny* `r citep(citation("shiny"))`, *rvinecopulib* `r citep(citation("rvinecopulib"))`, *hablar* `r citep(citation("hablar"))`, *tmvnsim* `r citep(citation("tmvnsim"))`, *paleotree* `r citep(citation("paleotree"))`, *sjmisc* [@R-sjmisc], *janitor* `r citep(citation("janitor"))`, *knitcitations* `r citep(citation("knitcitations"))`, *pastecs* `r citep(citation("pastecs"))`, *zoo* `r citep(citation("zoo"))`, *ggpubr* `r citep(citation("ggpubr"))`, *ggplotify* `r citep(citation("ggplotify"))`, *stringi* `r citep(citation("stringi"))`, *reticulate* `r citep(citation("reticulate"))`, *ggrepel* `r citep(citation("ggrepel"))`, *Pandoc* `r citep("https://pandoc.org/index.html")`.

*Stack Overflow* `r citep("https://stackoverflow.com/questions")`, *Datanovia* `r citep("https://www.datanovia.com/en/")`, `r citet("10.1007/978-3-319-23796-1")`.


*`r table_nums("challenges")`*

```{r challenges, echo=FALSE, fig.cap=table_nums("challenges"), message=FALSE, warning=FALSE, eval=T}

study1 <- c("Authors_1",
            "Topic",
            "Method")

study2 <- c("Authors_2",
            "Topic",
            "Method")

V <- cbind(study1,study2)
V <- as.data.frame(t(V))
colnames(V) <- c("Authors","Topic","Model")

f <- flextable(V)

f <- width(f, j = 1, width = 1.5)
f <- width(f, j = 2, width = 2.5)
f <- width(f, j = 3, width = 2.5)
f <- flextable::font(f, fontname = "Times New Roman",part = "all")
f <- flextable::fontsize(f, size=12,part = "all")
f <- bold(f, bold = TRUE, part = "header")

f

ch_cap <- table_nums("challenges")

```


<br/><br/>

## [Literature review]


# Data


```{r positions, message=FALSE, warning=FALSE, paged.print=TRUE,fig.cap = pos, out.width="80%", eval=T, echo=F}

Survey <- read_delim("D:/....csv",delim=";",locale=locale(encoding = "UTF-8", decimal_mark = "."))

names(Survey) <- Survey[1,]
Survey <- Survey[-c(1,2),-9]


l <- as.list(seq(1,8,1))

Role <- do.call(cbind,lapply(l, function(x){
  y <- ifelse(!is.na(Survey[,x]),names(Survey)[x],NA)
  return(y)
}))

Role_check <- Role[apply(Role,1,function(x)any(!is.na(x))),]

R <- melt(Role)
R <- R[!is.na(R$value),]

R <- within(R,
            value <- factor(value,
                            levels=names(sort(table(value),decreasing=F))))

Rt <- as.data.frame(table(R$value))
Rt$Freq <- as.numeric(Rt$Freq)

names(Rt) <- c('role','share')

p <- ggplot(Rt,aes(x=role,y=share,fill=role))+geom_bar(position="dodge", stat="identity")+ scale_fill_brewer(palette="Blues")+ theme(legend.position="none",panel.background = element_rect(fill = NA),panel.ontop =TRUE,panel.grid.major = element_blank())+coord_flip()

p+labs(x="role",y="share")

pos <- figure_nums("positions")


```


```{r markets, message=FALSE, warning=FALSE,fig.cap = mar, out.width="80%", eval=T, echo=F}

Eve <- read_delim("D:/...csv",delim=";",locale=locale(encoding = "UTF-8", decimal_mark = "."))
Eve <- Eve[-1,-c(1,3,4,105:108)]
Eve <- t(Eve)
colnames(Eve) <- Eve[1,]
Eve <- Eve[-1,]
G <- Eve[,11:17]

l <- as.list(seq(1,7,1))

Market <- do.call(cbind,lapply(l, function(x){
  y <- ifelse(!is.na(G[,x]),names(G)[x],NA)
  return(y)
}))

Market_check <- Market[apply(Market,1,function(x)any(!is.na(x))),]

R <- melt(Market)
R <- R[!is.na(R$value),]

R <- within(R,
            value <- factor(value,
                            levels=names(sort(table(value),decreasing=F))))


Rt <- as.data.frame(table(R$value))
Rt$Freq <- as.numeric(Rt$Freq)
names(Rt) <- c('market','quantity')

p <- ggplot(Rt,aes(x=market,y=quantity,fill=market))+geom_bar(position="dodge", stat="identity")+ scale_fill_brewer(palette="Blues") + theme(legend.position="none",panel.background = element_rect(fill = NA),panel.ontop =TRUE,panel.grid.major = element_blank())+
  coord_flip()
p+labs(x="market",y="quantity")

mar <- figure_nums("markets")

```

```{r message=FALSE, warning=FALSE, include=FALSE, eval=T, echo=F}

Rus <- as.data.frame(Eve[,20:21])

l <- list(1,2)

Russia <- do.call(cbind,lapply(l, function(x){
  y <- ifelse(!is.na(Rus[,x]),names(Rus)[x],NA)
  return(y)
}))

Russia_check <- Russia[apply(Russia,1,function(x)any(!is.na(x))),]

```


```{r e-commerce, message=FALSE, warning=FALSE, fig.cap = ecom, out.width="80%", eval=T, echo=F}

E <- as.data.frame(Eve[,23:26])

E$noanswer <- ifelse(is.na(E[,1])&is.na(E[,2])&is.na(E[,3]),1,E$noanswer)

l <- as.list(seq(1,4,1))

Commerce <- do.call(cbind,lapply(l, function(x){
  y <- ifelse(!is.na(E[,x]),names(E)[x],NA)
  return(y)
}))

Commerce_check <- Commerce[apply(Commerce,1,function(x)any(!is.na(x))),]

C <- melt(Commerce)
C <- C[!is.na(C$value),]

C <- within(C,
            value <- factor(value,
                            levels=names(sort(table(value),decreasing=F))))


Rt <- as.data.frame(table(C$value))
Rt$Freq <- as.numeric(Rt$Freq)
names(Rt) <- c('ecommerce','quantity')

p <- ggplot(Rt,aes(x=ecommerce,y=quantity,fill=ecommerce))+geom_bar(position="dodge", stat="identity")+ scale_fill_brewer(palette="Blues") + theme(legend.position="none",panel.background = element_rect(fill = NA),panel.ontop =TRUE,panel.grid.major = element_blank())+ scale_x_discrete(labels=c('no information', 'not active', 'plans to work', 'is currently working'))+
  coord_flip()
p+labs(x="",y="quantity")

ecom <- figure_nums("e-commerce")

```


```{r rank, message=FALSE, warning=FALSE, fig.cap = rank, out.width="80%", eval=T, echo=F}

E <- as.data.frame(Eve[,28:30])

E$other <- ifelse(is.na(E[,1])&is.na(E[,2]),1,E$other)

l <- list(1,2,3)

Rank <- do.call(cbind,lapply(l, function(x){
  y <- ifelse(!is.na(E[,x]),names(E)[x],NA)
  return(y)
}))

Rank_check <- Rank[apply(Rank,1,function(x)any(!is.na(x))),]

C <- melt(Rank)
C <- C[!is.na(C$value),]

C <- within(C,
            value <- factor(value,
                            levels=names(sort(table(value),decreasing=F))))


Rt <- as.data.frame(table(C$value))
Rt$Freq <- as.numeric(Rt$Freq)
names(Rt) <- c('rank','quantity')

p <- ggplot(Rt,aes(x=rank,y=quantity,fill=rank))+geom_bar(position="dodge", stat="identity",width=0.5)+ scale_fill_brewer(palette="Blues") + theme(legend.position="none",panel.background = element_rect(fill = NA),panel.ontop =TRUE,panel.grid.major = element_blank())+
  coord_flip()
p+labs(x="factor",y="quantity")

rank <- figure_nums("rank")


```


### [Saple]


```{r country, message=FALSE, warning=FALSE, out.width="80%", echo=F, include=F, eval=T, echo=F}

Sales <- read_delim("D:...csv",delim=";",locale=locale(encoding = "UTF-8", decimal_mark = "."))

colnames(Sales)[2] <- 'Company'
colnames(Sales)[4] <- 'Website'
colnames(Sales)[5] <- 'Main'
colnames(Sales)[6] <- 'Special'

Sales <- as.data.frame(Sales)

Snew <- Sales[,-c(1,4)]

Snew <- Snew[rowSums(is.na(Snew))!=28,]

for (i in c(1:3,5:ncol(Snew))) {
  while(length(ind <- which(is.na(Snew[,i]))) > 0){Snew[,i][ind] <- Snew[,i][ind -1]}
}

S <- Snew %>% distinct(Company,.keep_all = T)

n <- as.list(paste(rep(seq(2020,2017,-1),each=4),rep(seq(4,1,-1),times=4),sep = "Q"))

n[[1]] <- NULL
n[[1]] <- NULL
n[[13]] <- NULL
n[[13]] <- NULL

names(S)[5:16] <- paste(n,"Sales",sep = ".")
names(S)[17:28] <- paste(n,"Assets",sep=".")

S[,5:28] <- do.call(cbind,lapply(S[,5:28],function(x){
  y <- gsub("n.a.",NA,x)
  y <- as.data.frame(as.numeric(gsub(" ","",y)))
  return(y)
}))

S <- as.data.frame(S)

Sset <- S[!is.na(S[,6])&!is.na(S[,18]),] 

Sset <- Sset[Sset[,18]<10000,] 

Sset$Country <- as.factor(Sset$Country)
p <- as.data.frame(table(Sset$Country))
p$Freq <- as.numeric(p$Freq)
p$Percentage <- 100*p$Freq/nrow(Sset)
colnames(p)[1] <- 'country'
p <- p[order(-p$Percentage),]
p <- as_tibble(p)
p <- p %>% column_to_rownames(var='country')
phor <- as.data.frame(t(p))

l <- list(1,2)

phor$other <- do.call(rbind,lapply(l,function(x) {
  a <- sum(p[,x][9:nrow(p)])
  return(a)
}))

p <- as.data.frame(t(phor))
pnew <- p[c(1:8,nrow(p)),]

setDT(pnew, keep.rownames = TRUE)[]

names(pnew)[1] <- "country"

```


```{r,fig.cap=cntr, eval=T}

p <- pnew %>% arrange(Percentage)
ggplot(data=pnew, aes(x=reorder(countryrus, Percentage), y=Percentage, fill=factor(countryrus)))+
       coord_flip()+
       geom_bar(position="dodge",stat="identity")+
       scale_fill_brewer(palette="Blues")+
       theme(legend.position="none",panel.background = element_rect(fill = NA),panel.ontop =TRUE,panel.grid.major = element_blank())+
  labs(y="доля, %",x="Place")

cntr <- figure_nums("country")

```


```{r, message=FALSE, warning=FALSE, echo=F, include=F, eval=T}

Industry <- subset(Snew, Company %in% Sset$Company)

Industry$Special <- ifelse(!is.na(Industry$Special),Industry$Special,"no data")

Industry$Special <- as.factor(Industry$Special)

p <- as.data.frame(table(Industry$Special))
p$Freq <- as.numeric(p$Freq)
p$Percentage <- 100*p$Freq/nrow(Industry)
colnames(p)[1] <- 'industry'
p <- p[order(-p$Percentage),]
p <- as_tibble(p)
p <- p %>% column_to_rownames(var='industry')
phor <- as.data.frame(t(p))

l <- list(1,2)

phor$other <- do.call(rbind,lapply(l,function(x) {
  a <- sum(p[,x][9:nrow(p)])
  return(a)
}))

p <- as.data.frame(t(phor))
pnew <- p[c(1:8,nrow(p)),]

setDT(pnew, keep.rownames = TRUE)[]

names(pnew)[1] <- "industry"

```


```{r, fig.cap=indstr,out.width = "120%", eval=T}

p <- pnew %>% arrange(Percentage)
ggplot(data=pnew, aes(x=reorder(industryname, Percentage), y=Percentage, fill=factor(industryname)))+
       coord_flip()+
       geom_bar(position="dodge",stat="identity")+
       scale_fill_brewer(palette="Blues")+
       theme(legend.position="none",panel.background = element_rect(fill = NA),panel.ontop =TRUE,panel.grid.major = element_blank())+
  labs(y="share, %",x="industry")

indstr <- figure_nums("industry")


```


### [Data prepocessing]

```{r number, echo = F,results='hide',message=FALSE,out.width = "70%",fig.cap = num, eval=T}

l <- as.list(seq(5,15,1))

M <- do.call(cbind,lapply(l,function(x){
  y <- as.data.frame(Sset[,x]-Sset[,x+1])
  names(y) <- paste0(names(Sset[x]),"Growth")
  return(y)
}))

S <- cbind(Sset,M)

fviz_nbclust(S[,c(6,18)], kmeans, method = "silhouette")+xlab("number of clusters")+
  ylab("average silhouette width")+labs(title="")

num <- figure_nums("number")

```


```{r cluster, echo=F, message=FALSE, warning=FALSE, out.width="70%", results='hide',fig.cap = clus, eval=T}

k <- eclust(S[,c(6,18)],"kmeans",k=2,graph=F)

for (i in 1:length(k$cluster)){
  k$cluster[[i]] <- ifelse(k$cluster[[i]]==1,3,k$cluster[[i]])
}

for (i in 1:length(k$cluster)){
  k$cluster[[i]] <- k$cluster[[i]]-1
}

fviz_cluster(k,labelsize = 0,legend.title="cluster number")+theme(panel.background = element_rect(fill = "white", colour = "grey50"))+xlab("revenue")+ylab("assets")+scale_colour_manual(values = rev(brewer.pal(2,"Blues")))+scale_fill_brewer(palette="Blues")+labs(title="")

clus <- figure_nums("cluster")


```


$$Distance=\left\lvert\frac{Sales_{1i,t_{j}}}{Assets_{1i,t_{j}}}-\frac{Sales_{2j,t_{k}}}{Assets_{2j,t_{k}}}\right\rvert\leqslant5\%\frac{Sales_{1i,t_{j}}}{Assets_{1i,t_{j}}},$$ {#eq:eqn1}

(`r figure_nums("net", display = "cite")`).

```{r, eval=T}

S$Cluster <- k$cluster

S <- move_columns(S,Cluster,.after=Special)

Sbase <- S[,-c(17,29)]

n[[11]] <- NULL

Data <- Sbase[,6:38]
Data <- Data[,order(names(Data),decreasing = F)]
Sbase1 <- cbind(Sbase[,1:5],Data)

# Create companies' label data

a1 <- letters
a2 <- LETTERS
a3 <- intToUtf8(as.character(161:255), multiple=TRUE)[c(7,21,22,55,56)]

Sbase1$Label <- c(a1,a2,a3)

Sdata <- Sbase1 %>%
  gather(names(Sbase1[,endsWith(colnames(Sbase1), ".Sales")|endsWith(colnames(Sbase1), ".Assets")|endsWith(colnames(Sbase1), ".SalesGrowth")]), key = "variable", value = "value")

Sdata <- Sdata %>% separate(variable, c("quarter","indicator"))

Slong <- long_panel(Sbase1, suffix=".", prefix=NULL, id="Company", begin="2017Q4", end="2020Q2", label_location="beginning", periods = c("2017Q4","2018Q1","2018Q2","2018Q3","2018Q4","2019Q1","2019Q2","2019Q3","2019Q4","2020Q1","2020Q2"))

names(Slong)[2] <- 'Quarter'

Slong$Share <- Slong$Sales/Slong$Assets

```


```{r, eval=T}

# Data frame creation
n <- n %>% paleotree::reverseList()
n <- n[[1]]

r <- lapply(n,function(x) {
  y <- Slong[Slong$Quarter<x,]
  y <- y[!is.na(y$Share)&!is.na(y$SalesGrowth),]
  y1 <- y[y$Cluster==1,]
  y2 <- y[y$Cluster==2,]
  z <- difference_full_join(y1,y2,by="Share",max_dist=5*y1$Share/100,distance_col="Distance")
  u <- z[!is.na(z$SalesGrowth.x)&!is.na(z$SalesGrowth.y),]
  u$Quarter <- x
  setnames(u,"Company.y","Company")
  return(u)
})

t <- r %>% reduce(rbind)
r <- left_join(t,Slong,by=c("Company","Quarter"))

r <- r[order(r$Quarter,decreasing = F),]

r <- unique(setDT(r), 
       by = c('Company.x', 'Quarter.x', 'Company', 'Quarter.y'))

U <- r %>% ungroup() %>% dplyr::select('SalesGrowth.x', 'SalesGrowth.y', 'SalesGrowth', 'Quarter','Quarter.x','Quarter.y')
U <- U[!is.na(U$SalesGrowth),]



```



```{r}

Net <- r %>% ungroup() %>% dplyr::select('Company.x', 'Company', 'Quarter.x', 'Quarter.y', 'Distance')
setnames(Net,"Company","Company.y")

Net$from <- paste(Net$Company.x,Net$Quarter.x)
Net$to <- paste(Net$Company.y,Net$Quarter.y)

Edges <- Net %>% ungroup() %>% dplyr::select(from, to, Distance)

Edges <- Edges[Edges$from!="NA NA",]

Names <- Slong %>% dplyr::select(Company, Cluster, Quarter, Share, Label)

Names <- Names[!is.na(Names$Share),]

Names$id <- paste(Names$Company,Names$Quarter)

Vertices <- Names %>% ungroup() %>% dplyr::select(id, Cluster, Share, Label, Company)

```


```{r network, echo=F, message=FALSE, warning=FALSE, fig.width = 25.2, fig.height = 18, results='hide', fig.cap = network_graph, eval=T}

set.seed(2)

#Check

net <- graph_from_data_frame(d=Edges, vertices=Vertices, directed=T)

# Generate colors based on cluster:
colrs <- c(adjustcolor("red", alpha=0.5), adjustcolor("lightblue3", alpha=0.5))
V(net)$color <- colrs[V(net)$Cluster]

V(net)$size <- V(net)$Share*9

V(net)$label.color <- "black"

# Set edge width based on Distance:
E(net)$width <- E(net)$Distance

#change arrow size and edge color:
E(net)$arrow.size <- .2
E(net)$color <- adjustcolor("grey20", alpha=0.5)

V(net)$label <- V(net)$Label

# We can even set the network layout:
plot(net, vertex.label=ifelse(V(net)$Share>1.5,V(net)$label,NA),vertex.label.cex=2, edge.arrow.size=0,bty='T') 

op <- par(cex = 2,mar=c(9,8,0,2),xpd=TRUE)

legend(x=-1.9, y=-1, c("Cluster 1","Cluster 2"), pch=21, col="#777777", pt.bg=colrs, pt.cex=1.5, bty="n", ncol=1, title = expression(bold("Notation:")), text.font=3)

legend(x=-1.5, y=-1, unique(V(net)$Company[V(net)$Share>1.5]), pch=c(unique(V(net)$label[V(net)$Share>1.5])), col="grey20", pt.cex=1.4, bty="n", ncol=3, title = expression(bold("coefficient")), text.font=3, text.width = 1.2)

network_graph <- figure_nums("net")

```



```{r gr, echo=F, message=FALSE, warning=FALSE, fig.width = 7, fig.height = 5, results='hide',fig.cap = growth, eval=T}

Slong$Cluster <- as.factor(Slong$Cluster)

ggplot(Slong, aes(x=Quarter, y=SalesGrowth, color = Cluster))+geom_point(size=2, alpha=0.5)+scale_color_brewer(palette="Set1")+
  labs(y=paste0("sales growth","\U20AC"),x="quarter",colour = "cluster")+ theme_classic()+
  geom_hline(yintercept=0)+
  theme(axis.text = element_text(size = 8))

growth <- figure_nums("SalesGrowth")

```

```{r distr, echo=F, message=FALSE, warning=FALSE, fig.width = 7, fig.height = 5, results='hide',fig.cap = distribution_sales, eval=T}

S1 <- r[!is.na(r$SalesGrowth.x)&!is.na(r$SalesGrowth.y)&!is.na(r$Distance),]


ggplot(S1, aes(x=S1$SalesGrowth.x, y=S1$SalesGrowth.y,size=80*S1$Distance)) +
  geom_point(alpha=0.3, color="darkslateblue",pch=1)+
  labs(x="sales growth cluster 1, млн \U20AC", y="sales growth cluster 2, млн \U20AC", caption=expression(paste(Delta, "difference")), size=expression(80%*%Delta))+
  geom_hline(yintercept=0)+
  theme(plot.caption=element_text(size=9, hjust=0, margin=margin(t=30)), axis.title=element_text(size=10,face = "bold"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), legend.background = element_blank(),legend.key = element_rect(colour = "transparent", fill = "white"))


distribution_sales <- figure_nums("distribution")


```


*`r table_nums("variables")`*

```{r vars, fig.cap = var_cap}

variable1 <- c("SalesGrowth.x",
            "cluster 1 sales growth")

variable2 <- c("SalesGrowth.y",
            "cluster 2 sales growth")

V <- cbind(variable1,variable2,variable3)
V <- as.data.frame(t(V))
colnames(V) <- c("Label","Description")

B <- stat.desc(U[,1:3], basic=F, desc=F)
B <- round(B,digits=1)
B <- format(B,nsmall = 1,big.mark = " ")
B <- as.data.frame(t(B))
B <- setDT(B, keep.rownames = T)[]
setnames(B,"rn","Обозначение")
B <- B[,c(1,5:7)]
names(B) <- c('Label','Median','Mean','Standard deviation')

W <- cbind(V, B[,-1])

f <- flextable(W)

f <- width(f, j = 1, width = 1.2)
f <- width(f, j = 2, width = 2.5)
f <- width(f, j = 3, width = 1)
f <- width(f, j = 4, width = 0.9)
f <- flextable::font(f, fontname = "Times New Roman",part = "all")
f <- flextable::fontsize(f, size=11,part = "all")
f <- bold(f, bold = TRUE, part = "header")
f <- italic(f, part = "body",j=1, italic=T)
f <- flextable::compose(f, part="header",j="Standard deviation",value=as_paragraph("\u03C3"))

f

var_cap <- table_nums("variables")

```


```{r}

U <- U %>% convert(num())

Test <- U[U$Quarter>"2019Q4",]
Train <- U[U$Quarter<="2019Q4",]

Test <- Test[,1:3]
Train <- Train[,1:3]

```

```{r}

use_python("D:\\Programs\\anaconda3\\python.exe")
matplotlib <- import("matplotlib")
matplotlib$use("Agg", force = TRUE)

```

```{python}

Train = r.Train
Test = r.Test

```



```{python, include=F}

import numpy as np
import matplotlib as mpl
from matplotlib import pyplot as plt
from matplotlib import cm
from sklearn.preprocessing import QuantileTransformer
from sklearn.preprocessing import minmax_scale

X=Train[['SalesGrowth.x','SalesGrowth.y']]
X=X.values
y_full = Train.loc[:,'SalesGrowth']
y_full = y_full.values
X_test=Test[['SalesGrowth.x','SalesGrowth.y']]
X_test=X_test.values
y_test = Test.loc[:,'SalesGrowth']
y_test = y_test.values


distributions = [('original data', X, X_test), ('quantile transformed data (uniform distribution)', QuantileTransformer(output_distribution='uniform').fit_transform(X), QuantileTransformer(output_distribution='uniform').fit_transform(X_test)),]


y = minmax_scale(y_full)
y_2 = minmax_scale(y_test)

cmap = getattr(cm, 'blues_r', cm.seismic_r)

def create_axes(title, figsize=(11.43, 4.29)):
    fig = plt.figure(figsize=figsize)
    fig.suptitle(title)

    # define the axis for the first plot
    left, width = 0.1, 0.23
    bottom, height = 0.1, 0.7
    bottom_h = height + 0.15
    left_h = left + width + 0.02

    rect_scatter = [left, bottom, width, height]
    rect_histx = [left, bottom_h, width, 0.1]
    rect_histy = [left_h, bottom, 0.05, height]

    ax_scatter = plt.axes(rect_scatter)
    ax_histx = plt.axes(rect_histx)
    ax_histy = plt.axes(rect_histy)
    
    # define the axis for the second plot
    left = width + left + 0.25
    left_h = left + width + 0.02

    rect_scatter = [left, bottom, width, height]
    rect_histx = [left, bottom_h, width, 0.1]
    rect_histy = [left_h, bottom, 0.05, height]

    ax_scatter_zoom = plt.axes(rect_scatter)
    ax_histx_zoom = plt.axes(rect_histx)
    ax_histy_zoom = plt.axes(rect_histy)
    
    # define the axis for the Train colorbar
    left_train, width_train = left - 0.18, 0.01

    rect_colorbar_train = [left_train, bottom, width_train, height]
    ax_colorbar_train = plt.axes(rect_colorbar_train)
    
    # define the axis for the Test colorbar
    left_test, width = width + left + 0.07, 0.01

    rect_colorbar_test = [left_test, bottom, width, height]
    ax_colorbar_test = plt.axes(rect_colorbar_test)

    return ((ax_scatter, ax_histy, ax_histx),
            (ax_scatter_zoom, ax_histy_zoom, ax_histx_zoom),
            ax_colorbar_train, ax_colorbar_test)
            
            
def plot_distribution(axes, X, y, hist_nbins=50, title="",
                      x0_label="", x1_label=""):
    ax, hist_X1, hist_X0 = axes

    ax.set_title(title)
    ax.set_xlabel(x0_label)
    ax.set_ylabel(x1_label)

    colors = cmap(y)
    ax.scatter(X[:, 0], X[:, 1], alpha=0.5, marker='o', s=9, lw=0, c=colors)

    ax.spines['top'].set_visible(False)
    ax.spines['right'].set_visible(False)
    ax.get_xaxis().tick_bottom()
    ax.get_yaxis().tick_left()
    ax.spines['left'].set_position(('outward', 20))
    ax.spines['bottom'].set_position(('outward', 0))
    
    hist_X1.set_ylim(ax.get_ylim())
    hist_X1.hist(X[:, 1], bins=hist_nbins, orientation='horizontal',
                 color='grey', ec='grey')
    hist_X1.axis('off')

    hist_X0.set_xlim(ax.get_xlim())
    hist_X0.hist(X[:, 0], bins=hist_nbins, orientation='vertical',
                 color='grey', ec='grey')
    hist_X0.axis('off')
       
    
    
def make_plot(item_idx):
    title, X, X_test = distributions[item_idx]
    ax_zoom_train, ax_zoom_test, ax_colorbar_train, ax_colorbar_test = create_axes(title)
    axarr = (ax_zoom_train, ax_zoom_test)
    plot_distribution(ax_zoom_train, X, y, hist_nbins=200,
                      x0_label="SalesGrowth.x",
                      x1_label="SalesGrowth.y",
                      title="Train set")
    
    plot_distribution(ax_zoom_test, X_test, y_2, hist_nbins=200,
                      x0_label="SalesGrowth.x",
                      x1_label="SalesGrowth.y",
                      title="Test set")

    norm = mpl.colors.Normalize(y_full.min(), y_full.max())
    mpl.colorbar.ColorbarBase(ax_colorbar_train, cmap=cmap,
                              norm=norm, orientation='vertical',
                              label='SalesGrowth')
    
    norm = mpl.colors.Normalize(y_test.min(), y_test.max())
    mpl.colorbar.ColorbarBase(ax_colorbar_test, cmap=cmap,
                              norm=norm, orientation='vertical',
                              label='SalesGrowth')


```


```{python, fig.width = 14, fig.height = 10}

make_plot(0)
plt.show()

```
*`r figure_nums("original")`*

<br/><br/>

```{python, fig.width = 14, fig.height = 10}

make_plot(1)
plt.show()

```
*`r figure_nums("transformed")`*

<br/><br/>

```{r}

a <- import("sklearn.preprocessing", convert=F)

set.seed(2)

Train_set <- Train
Test_set <- Test

Train_set <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(Train_set))$fit_transform(Train_set)
Test_set <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(Test_set))$fit_transform(Test_set)

Test_set <- as.matrix(Test_set)
Test_set <- as.data.frame(Test_set)
names(Test_set) <- names(Test)

Train_set <- as.matrix(Train_set)
Train_set <- as.data.frame(Train_set)
names(Train_set) <- names(Train)

Train <- as.data.frame(Train)
Test <- as.data.frame(Test)

```

```{r}

Train <- do.call(cbind, lapply(Train, function(x) {
  x <- as.numeric(x)
}))


```


## [Model]

```{r}

M <- do.call(cbind, lapply(U[,4:6], function(x) {
  y <- as.yearqtr(x)
  y <- as.data.frame(y)
  return(y)
}))

names(M) <- paste(names(U[,4:6]),"date",sep="_")

Full <- cbind(U, M)

Full$prop4 <- Full$Quarter.y_date-Full$Quarter.x_date

Full$prop5 <- Full$Quarter_date-Full$Quarter.y_date

Prop4 <- 4*max(Full$prop4)
Prop5 <- 4*max(Full$prop5)

```


### [Assumptions]


```{r, eval=T, include=F}

kendall.tau(Train_set$SalesGrowth.x, Train_set$SalesGrowth.y)

BiCopIndTest(Train_set$SalesGrowth.x,Train_set$SalesGrowth.y)

```


# [Results]


```{r, eval=T}

py_set_seed(2)

l <- list("bb1","bb6","bb7","bb8","clayton","frank","gaussian","gumbel","indep","joe","t","tll")

sk <- import("sklearn.preprocessing", convert = FALSE)
# Создаем копию данных, уже переведенную в uniform
Train_trans <- Train
Train_trans[,1:2] <- py_to_r(sk$QuantileTransformer(output_distribution='uniform')$fit_transform(Train[,1:2]))


M_R2 <- lapply(l, function(x){
  
  cop <- list(type = c("Regression","Classification"),
              library = "rvinecopulib",
              loop = NULL) 

prm <- data.frame(parameter="family_set",
                  class = "string",
                  label = "Families")

cop$parameters <- prm

# give families of a copulas

copgrid <- data.frame(c(x)) 
names(copgrid) <- 'family_set'

cop$grid <- copgrid

# fitting parameters

copFit <- function(x,y, data, var_types, par_method, nonpar_method, selcrit, psi0, wts, param, lev, last, classProbs) {
    
  bicop(data = x, var_types = c("c", "c"),
        family_set = param$family_set, 
        par_method = "mle", 
        nonpar_method = "quadratic",
        selcrit = "aic", 
        psi0 = 0.95)
}
 
cop$fit <- copFit

# predicting parameters

copPred <- function(modelFit,newdata, preProc=NULL, submodels = NULL) {
  
  newdata1 <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(newdata))$fit_transform(newdata[,1:2])
  newdata1 <- as.matrix(newdata1)
  
  y <- cbind(predict(object=modelFit, newdata1, what="hfunc2"), predict(object=modelFit, newdata1, what="hfunc1"))
  
  z <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(y))$fit(newdata[,1:2])$inverse_transform(y)
  z <- as.matrix(z)
  return(z[,2])
  
}

cop$predict <- copPred

# probabilities

copProb <- function(modelFit, newdata, preProc=NULL, submodels = NULL) {
  
 newdata1 <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(newdata))$fit_transform(newdata[,1:2])
 newdata1 <- as.matrix(newdata1)
  
  y <- predict(object=modelFit, newdata1, what="hfunc1", type="probabilities")
  return(y)
  
}
  
cop$prob <- copProb


# Rsquared function

f1 <- function(data, lev = NULL, model = NULL) {
  # Принудительно преобразуем в числовой формат
  obs <- as.numeric(data$obs)
  pred <- as.numeric(data$pred)
  
  # Рассчитываем базовые компоненты
  ss_res <- sum((obs - pred)^2)
  ss_tot <- sum((obs - mean(obs))^2)
  
  # Избегаем деления на ноль
  if (ss_tot == 0) {
    r2 <- 0
  } else {
    r2 <- 1 - (ss_res / ss_tot)
  }
  
  c(Metric = r2)
}


set.seed(2)

fitControl <- trainControl(method = "timeslice", initialWindow = 150,horizon = 50,fixedWindow = F, verboseIter = T, savePredictions = T, summaryFunction = f1, returnResamp = "all")
  
set.seed(2)
Model_traditional <- train(x=Train_trans[,1:2],y=Train_trans[,3],
                   data=Train_trans,
                   method = cop,
                   trControl = fitControl,
                   tuneGrid = copgrid, 
                   metric="Metric")

return(Model_traditional)
  
})

```


```{r}

p <- lapply(M, function(x) {
  cbind(x$results, AIC(x$finalModel), BIC(x$finalModel), logLik(x$finalModel), paste0(x$finalModel[2]))
})

t <- data.frame(matrix(unlist(p), nrow=length(l), byrow=T))

names(t) <- names(p[[1]])

```


*`r table_nums("models")`*

```{r results, echo=FALSE, fig.cap=table_nums("models"), message=FALSE, warning=FALSE, eval=T}

t[,-1] <- lapply(t[,-1], function(x) {
  x <- as.numeric(x)
  x <- round(x, digits=3)
})

t[,-1] <- round(t[,-1],digits=3)

t$Copula <- c("Clayton-Gumbel","Джо-Gumbel","Joe-Clayton","Joe-Frank","Clayton","Frank","Gaussian","Gumbel","Independence","Joe","t-copula","nonparametric copula")

setnames(t,"AIC(x$finalModel)","AIC")
setnames(t,"BIC(x$finalModel)","BIC")
setnames(t,"logLik(x$finalModel)","LogLikelihood")
setnames(t,"paste0(x$finalModel[2])","rotation")
setnames(t, "Copula","Moled")
setnames(t, "rotation","Angle")

t1 <- t %>% ungroup() %>% dplyr::select('Model', 'Angle', 'AIC', 'BIC', 'LogLikelihood')

f <- flextable(t1)

f <- flextable::font(f, fontname = "Times New Roman",part = "all")
f <- flextable::fontsize(f, size=11,part = "all")
f <- bold(f, bold = TRUE, part = "header")
f <- bold(f, j = 1, bold = TRUE, part = "body")

f <- flextable::footnote(f, i = 12, j = "Model", value = as_paragraph(c("estimated with nonparametric transformation kernel")),ref_symbols = c("b"))

f <- autofit(f)

f

ch_cap <- table_nums("model")

```

<br/><br/>

*`r table_nums("metrics")`*

```{r metrics, echo=FALSE, fig.cap=table_nums("metrics"), message=FALSE, warning=FALSE, eval=T}

t2 <- t %>% ungroup() %>% dplyr::select('Model', 'Angle', 'RMSE', 'RMSESD', 'Rsquared', 'RsquaredSD', 'MAE', 'MAESD')


f <- flextable(t2)

f <- flextable::font(f, fontname = "Times New Roman",part = "all")
f <- flextable::fontsize(f, size=11,part = "all")
f <- bold(f, bold = TRUE, part = "header")
f <- bold(f, j = 1, bold = TRUE, part = "body")

f <- flextable::footnote(f, i = 12, j = "Model", value = as_paragraph(c("estimated with nonparametric transformation kernel")),ref_symbols = c("b"))

f <- flextable::compose(f, part="header",j="RMSESD",value=as_paragraph(as_b("\U03C3"),as_sub("RMSE")))
f <- flextable::compose(f, part="header",j="RsquaredSD",value=as_paragraph(as_b("\U03C3(R"),as_sup("2"),")"))
f <- flextable::compose(f, part="header",j="MAESD",value=as_paragraph(as_b("\U03C3"),as_sub("MAE")))
f <- flextable::compose(f, part="header",j="Rsquared",value=as_paragraph(as_b("R"),as_sup("2")))

f <- width(f, j = 1, width = 2.1)
f <- width(f, j = 2, width = 1.2)
f <- width(f, j = 3, width = 0.6)
f <- width(f, j = 4, width = 0.6)
f <- width(f, j = 5, width = 0.5)
f <- width(f, j = 6, width = 0.5)
f <- width(f, j = 7, width = 0.6)
f <- width(f, j = 8, width = 0.5)

f

ch_cap <- table_nums("metrics")

```

```{r}
setnames(t, "Модель копулы","copula")
```


```{r comparison, eval=T, fig.width = 7.7, fig.height = 5.5, fig.cap=comp_cop}

ggplot(t, aes(x=Rsquared, y=LogLikelihood, size=RMSE, color=AIC, label=copula)) +
  geom_point(alpha=0.6, pch=16)+
  labs(x=expression(R^2), y="LogLikelihood", size="RMSE")+
  geom_hline(yintercept=0)+
  theme(plot.caption=element_text(size=9, hjust=0, margin=margin(t=30)), axis.title=element_text(size=10,face = "bold"),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), legend.background = element_blank(),legend.key = element_rect(colour = "transparent", fill = "white"))+ geom_label_repel(size=3, color="black")


comp_cop <- figure_nums("model_comparison")

```


```{r, eval=F}

# run for model details

h <- list(type = c("Regression","Classification"),
              library = "rvinecopulib",
              loop = NULL) 

prm <- data.frame(parameter=c("theta","delta"),
                  class = c("c","c"),
                  label = c("theta","delta"))

h$parameters <- prm

# create grid

hgrid <- expand.grid(theta=seq(1,6,0.01),delta = seq(0,6,0.01))
names(hgrid) <- c('theta','delta')
h$grid <- hgrid

# fitting parameters

hFit <- function(x,y,data, cond_var, family, rotation, parameters, inverse, var_types, wts, param, lev, last, classProbs) {

bicop_dist(family="bb7",
       rotation = 180,
       parameters=c(param$theta,param$delta), 
       var_types = c("c","c")
       )
}
 
h$fit <- hFit

# predicting parameters

hPred <- function(modelFit, newdata, cond_var, family, rotation, parameters, inverse, var_types, preProc=NULL, submodels = NULL,param) {

  newdata1 <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(newdata))$fit_transform(newdata[,1:2])
  newdata1 <- as.matrix(newdata1)
  
  # predict values on the base of the copula model
  y <- cbind(predict(object=modelFit, newdata1, what="hfunc2"), predict(object=modelFit, newdata1, what="hfunc1"))
  z <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(y))$fit(newdata[,1:2])$inverse_transform(y)
  z <- as.matrix(z)
  return(z[,2])

}

h$predict <- hPred

# probabilities

hProb <- function(modelFit, newdata, preProc=NULL, submodels = NULL,type="probabilities",cond_var, family, rotation, parameters, inverse, var_types,param) {
 
  newdata1 <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(newdata))$fit_transform(newdata[,1:2])
  newdata1 <- as.matrix(newdata1)
  
  # predict values on the base of the copula model
  y <- cbind(predict(object=modelFit, newdata1, what="hfunc2", type="probabilities"), predict(object=modelFit, newdata1, what="hfunc1", type="probabilities"))
  z <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(y))$fit(newdata[,1:2])$inverse_transform(y)
  z <- as.matrix(z)
  return(z[,2]) 
 
}
  
h$prob <- hProb

```


```{r, include=T, eval=F}

set.seed(2)

fitControl <- trainControl(method = "timeslice", initialWindow = 150,horizon = 50,fixedWindow = F,savePredictions = T, verboseIter = T)
  
set.seed(2)
Joe_Clayton <- train(x=Train[,1:2],y=Train[,3],
                   data=Train,
                   method = h,
                   trControl = fitControl,
                   tuneGrid = hgrid, 
                   metric="Rsquared")

summary(Joe_Clayton)

```

```{r save_results, eval=F}

results <- Joe_Clayton$pred

save(results, file = "Results.Rda")

```


## [Model testing]

```{r, eval=F}

predicted_test <- cbind(predict(bicop_dist(family="bb7",
       rotation = 0,
       parameters=c(1,0), 
       var_types = c("c","c")
       ),newdata=Test_set[,1:2],what="hfunc2"),
       predict(bicop_dist(family="bb7",
       rotation = 0,
       parameters=c(1,0), 
       var_types = c("c","c")
       ),newdata=Test_set[,1:2],what="hfunc1"))

z <- a$QuantileTransformer(output_distribution='uniform', n_quantiles=nrow(predicted_test))$fit(Test[,1:2])$inverse_transform(predicted_test)
z <- as.matrix(z)

b <- as.data.frame(cbind(Test$SalesGrowth,z[,2]))
names(b) <- c("obs","pred")

defaultSummary(b)

```

# [Discussion]

## [Literature]

```{r, include=F, eval=T}

knitr::write_bib(c(.packages(), "bookdown"), "packages.bib")

write.bibtex(file="references.bib")

```

